\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
CP

\bcp{Richard: I get a little lost in this paragraph. Partly because I found the figure a bit confusing, partly because of the length of the paragraph. I think one fix might be to frontload your conclusion a bit with a topic sentence. E.g., start the paragraph with something like:
"For example, choosing a conference location with the goal of minimizing CO2e emissions from participants' travel results in trade-offs in who participates."}

>>>>

% \bcp{Richard: I get a little lost in this paragraph. Partly because I
% found the figure a bit confusing, partly because of the length of the
% paragraph. I think one fix might be to frontload your conclusion a bit
% with a topic sentence. E.g., start the paragraph with something like: "For
% example, choosing a conference location with the goal of minimizing CO2e
% emissions from participants' travel results in trade-offs in who
% participates."}
